Cooperative Control for Narrow Passage Traversal with an Ornithopter Micro Air Vehicle and Lightweight Ground Station

### 2012-10-10 manuscript.tex
Added some text

We also introduce a new ornithopter MAV, the 13 gram H$^2$Bird. It 
features clap and fling wings, improves upon a previous design by 
utilizing a carbon fiber airframe, tail rotor, and elevator, and carries a 
payload of 2.8 grams. We augment the ornithopter's built-in 
gyroscope-based control with a ground station, which has power and weight 
requirements appropriate for deployment on 30 gram a ground vehicle. The ground 
station provides heading estimates to the ornithoper by running a 
real-time motion tracking algorithm on a live video stream. This allows 
the ornithopter to reliably negotiate flight through narrow openings.

@@

\category{I.2.9}{Robotics}{Autonomous Vehicles}
\category{I.2.9}{Robotics}{Distributed Artificial Intelligence}[Multiagent systems] 
\category{I.2.9}{Robotics}{Vision and Scene Understanding}[Motion]

@@

\begin{equation}
\label{quat_error}
q_e = q'\otimes q_r
\end{equation}
\begin{equation}
\label{quat_angle}
\alpha = 2acos(q_{e,w})
\end{equation}
\begin{equation}
\label{quat_linearize}
Q_e = \alpha*q_e/sin(\alpha /2)
\end{equation}

@@

We determined the turning speed and turning radius of the H$^2$Bird 
experimentally using the response of the system to the input of a 90 
degree turn to the right. The results of this experiment are depicted in 
Figure \ref{fig:step_response}. The data for the experiment was gathered 
from the gyro data integrated on-board the H$^2$Bird. We used Matlab to 
fit a simple low-order model, $H(s) = \frac{0.94782}{1+0.61998s}$, of the 
turning system to the step response with the physical heading as the state 
and the heading setpoint as the input. We use this model in Section X to 
determine the backwards reachable set for navigating through the window in 
simulation.

The step response exhibits a rise time of approximately 1.4 seconds. The H
$^2$Bird flies at an average forward velocity of 1.2 m/s, so the estimated 
minimum turning radius of the robot is 1.07 meters.

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
%TODO(cameron)

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/flight_paths.pdf}
\caption{Plot of camera field-of-view and H$^2$Bird minimum turning radius 
cone, with experimental trials overlayed.}
\label{fig:flight_paths}
\end{figure}

We determined the backwards reachable set of initial states for sussessful 
window traversal both geometrically and in simulation. The results are 
shown in Figure X. The geometrically infeasible region is indicated in 
blue and was computed using the minimum turning radius and simple 
geometery. Both the regions in red and blue indicate the infeasible region 
determined in simulation. We executed the simulation on the fitted turning 
model described in Section \ref{sec:flight_control}, with a PID controller 
steering the system to the center of the window as the input. The 
infeasible region calculated in simulation is a superset of the 
geometrically infeasible region, and is closer to the true infeasible 
region of the real system.

The

>>>>

We also introduce a new ornithopter MAV, the 13 gram H$^2$Bird. It 
features clap and fling wings, improves upon a previous design by 
utilizing a carbon fiber airframe, tail rotor, and elevator, and carries a 
payload of 2.8 grams. We augment the ornithopter's built-in 
gyroscope-based control with a ground station, which has power and weight 
requirements appropriate for deployment on a ground vehicle. The ground 
station provides heading estimates to the ornithoper by running a 
real-time motion tracking algorithm on a live video stream. This allows 
the ornithopter to reliably negotiate flight through narrow openings.

@@

\category{I.2.9}{Robotics}{Autonomous Vehicles}
\category{I.2.9}{Robotics}{Distributed Artificial Intelligence}[Multiagent Systems]
\category{I.2.9}{Robotics}{Vision and Scene Understanding}[Motion]

@@

\begin{equation}
\label{quat_error}
q_e = q'\otimes q_r
\end{equation}

\begin{equation}
\label{quat_angle}
\alpha = 2acos(q_{e,w})
\end{equation}

\begin{equation}
\label{quat_linearize}
Q_e = \alpha*q_e/sin(\alpha /2)
\end{equation}

@@

We determined the turning speed and turning radius of the H$^2$Bird
experimentally using the response of the system to the step input of a
clockwise 90 degree turn. The results of this experiment are depicted in
Figure~\ref{fig:step_response}. The data for the experiment was gathered from
the integration of the H$^2$Bird's built in gyroscope data. We used Matlab to
fit a simple low-order model, $H(s) = \frac{0.94782}{1+0.61998s}$, of the
turning behavior to the step response with the physical heading as the state
and the heading set point as the input. This model serves as a simplification
of both the turning dynamics of the ornithopter and the on-board PID
controller regulating the actuator inputs to reach the desired orientation. We
use this model in Section~\ref{sec:visual_servoing} to determine the backwards
reachable region for navigating through the window in simulation.

The step response has a rise time of approximately 1.4 seconds. The H$^2$Bird
flies at an average forward velocity of 1.2 m/s, so the estimated minimum
turning radius of the robot is 1.07 meters. This flight speed is slower than
the maximum speed of the ornithopter to facilitate more reliable tracking.

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing}
%TODO(cameron)

\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.45\linewidth}
\centering
\includegraphics[width=\textwidth]{figures/flight_paths.pdf}
\caption{Plot of camera field-of-view and H$^2$Bird minimum turning radius 
cone, with experimental trials overlayed.}
\label{fig:flight_paths}
\end{minipage}
\end{figure*}

We determined the backwards reachable set of initial states for successful
window traversal both geometrically and in simulation. The results are shown
in Figure~\ref{fig:feasible_set}. The initial conditions that we chose are
spatially gridded in the camera viewing region at 0.05 meter increments and an
initial angular position perpendicular to the window plane. The geometrically
infeasible region is indicated in blue and was computed using the minimum
turning radius and simple geometry. Both the regions in red and blue indicate
the infeasible region determined in simulation. We simulated the turning model
described in Section~\ref{sec:flight_control}, with a PID controller steering
the system to the center of the window as the input. The infeasible region
calculated in simulation is a superset of the geometrically infeasible region.
The simulation is more realistic as the rotational damping during the turn and
the on-board PID controller cause the real system to react to inputs at a
non-constant angular velocity.

To verify the feasible region experimentally, we conducted trials at initial
distances in X meter increments from the window along the edges of the image
frame of the camera. We started each trial with an initial heading
perpendicular to the window plane. The results of the experiments are shown in
Figure~\ref{fig:flight_paths}.
